%-------------------------
% Resume in Latex
% Author: Rudra Patel
% Based on: https://github.com/jakegut/resume (which was itself based on https://github.com/sb2nov/resume)
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontawesome5}

\input{glyphtounicode}

% -------------------- FONT OPTIONS --------------------
% sans-serif
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% serif
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-1in} % Default was -.5in
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Subsection formatting
\titleformat{\subsection}{
  \vspace{-4pt}\scshape\raggedright\large
}{\hspace{-.15in}}{0em}{}[\color{black}\vspace{-8pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% -------------------- CUSTOM COMMANDS --------------------
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\setlength{\footskip}{4.08003pt}

% -------------------- START OF DOCUMENT --------------------
\begin{document}

% -------------------- HEADING --------------------
\begin{flushright}
  % \vspace{-4pt}
  \color{gray}
  \item
  Last Updated on September 12, 2024
\end{flushright}

\vspace{-5pt}

\begin{center}
    \textbf{\Huge \scshape Rudra Patel} \\ \vspace{1pt}
    \small 
    \faIcon{phone}
    +44 7824048693 $ $ 
    \faIcon{envelope}
    \href{mailto:work.rudra@aol.com}{\underline{work.rudra@aol.com}} $ $ 
    \faIcon{linkedin}
    \href{https://linkedin.com/in/ruudra03}{\underline{linkedin.com/in/ruudra03}} $ $
    \faIcon{github}
    \href{https://github.com/ruudra03}{\underline{github.com/ruudra03}}
\end{center}

% -------------------- WORK EXPERIENCE --------------------
\section{Work Experience}
\resumeSubHeadingListStart

        \resumeProjectHeading
        {\textbf{Build Macro} $|$ \footnotesize\emph{Software Engineer Intern}}{Sept 2024 -- Present}
        \resumeItemListStart
            \resumeItem{{\textit{Technologies:} \textbf{Angular, TypeScript, NodeJS, ExpressJS, SQL, BigQuery, Firebase, HTML, CSS, Git}}}
            \resumeItem{Building new project report pages for users, several already pushed into production.}
            \resumeItem{Creating and optimizing server endpoints in development for displaying dynamic data on the report pages.}
          \resumeItemListEnd

        \resumeProjectHeading
        {\textbf{Silverwing Technologies Pvt. Ltd.} $|$ \footnotesize\emph{Intern}}{Aug 2024}
        \resumeItemListStart
            \resumeItem{Completed several \textbf{NodeJS} challenges while being trained by senior team members.}
            \resumeItem{Interacted with backend developers while constantly learning and holding discussions with the team.}
          \resumeItemListEnd

        \resumeProjectHeading
        {\textbf{Tumlare Software Services} $|$ \footnotesize\emph{Software Engineer Intern}}{July 2024 -- Aug 2024}
        \resumeItemListStart
            \resumeItem{{\textit{Technologies:} \textbf{Vite, VueJS, JavaScript, NodeJS, Vuex, Axios, HTML, CSS, Sass, ChartJS, Git}}}
            \resumeItem{Created a frontend application with role-based user access and implemented state persistence.}
            \resumeItem{Built an interactive dashboard showing data insights using charts, tables, and tooltips for the app.}
            \resumeItem{Implemented RESTful API using \textbf{JSON-server} to mock endpoint requests, and used \textbf{Mockaroo} to generate placeholder data during development.}
          \resumeItemListEnd
    
        \resumeProjectHeading
        {\textbf{H.V. Sales} $|$ \footnotesize\emph{Associate Product Manager -- Part-time}}{Sept 2022 -- June 2024}
        \resumeItemListStart
            \resumeItem{Optimized product listings on several different marketplaces and the company's personal website, and also added more than 200 new seasonal products to the company's portfolio.}
            \resumeItem{Streamlined order fulfillment by introducing better inventory management solutions, reducing dispatch time.}
            \resumeItem{Assisted in implementing marketplace promotions for bestselling products, and analyzed customer trends and feedback to deliver better results.}
          \resumeItemListEnd
          
        \resumeProjectHeading
        {\textbf{University of Westminster} $|$ \footnotesize\emph{Student Helper}}{Mar 2024 -- Apr 2024}
        \resumeItemListStart
            \resumeItem{Worked on the development of an ontology-based framework for Scalable Evaluation of Text Summarisation (SETS Project funded by The Alan Turing Institute).}
            \resumeItem{Conducted literature review and data analysis, working alongside university professors and PhD students.}
            \resumeItem{Collaborated throughout the research, gaining experience in academic research.}
        \resumeItemListEnd
          
    \resumeSubHeadingListEnd

% -------------------- TECHNICAL SKILLS --------------------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small
    {\item{
     \textit{Languages: }{\textbf{Python}, \textbf{Java}, \textbf{JavaScript}, \textbf{TypeScript}, SQL, XML, R, \textbf{PHP}, Swift, Kotlin, \textbf{HTML}, \textbf{CSS}, Sass} \\

     \textit{Frameworks: }{\textbf{React}, \textbf{Vue.js}, \textbf{Angular}, \textbf{ExpressJS}, \textbf{Node.js}} \\
     
     \textit{Developer Tools: }{\textbf{Git}, \textbf{GitHub}, VS Code, Vite, \textbf{Firebase}, Xcode, Atelier B, ProB, Android Studio, RStudio, SQLite Studio, phpMyAdmin, Mockaroo, \textbf{Postman}, LTSA, JDK, NetBeans IDE, Visual Studio, Kali Linux, Draw.io, CyberDuck, Trello, Notion, \textbf{JSON-server}} \\
     
     \textit{Libraries: }{Axios, \textbf{JWT}, \textbf{Redux}, \textbf{Vuex}, Mongoose, Latex, SQLite, Chart.js} \\

     \textit{Database Management Systems: }{\textbf{MongoDB}, MySQL, PostgreSQL, \textbf{BigQuery}}
    }}
 \end{itemize}

% -------------------- EDUCATION --------------------
\section{Education}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {University of Westminster, London}{Sept 2021 -- July 2024}
      {Bachelor of Engineering in Software Engineering}{Awarded: \textbf{First Class Honours}}

  \resumeSubHeadingListEnd

% -------------------- Extra Curricular --------------------
\section{Extra Curricular \& Hobbies}
    \resumeSubHeadingListStart

        \resumeProjectHeading
            {\textbf{Westminster Working Cultures (WWC) UK @ University of Westminster}}{Sept 2024}
            
            With the goal of improving employability, enthusiastically connected and networked with students and professionals from different fields, and visited several workplaces in London and Bristol.
            
        \resumeProjectHeading
            {\textbf{EDI\&AI, AI UK Turing Fringe @ Westminster Research Communities}}{Mar 2024}
            
            Connected and networked with researchers working on innovative projects involving Data Science and Artificial Intelligence, and also got an opportunity to present the TuringWise Project (Final Year Project).

        \resumeProjectHeading
            {\textbf{Varsity Code @ University of Westminster}}{2022}

        \resumeProjectHeading
            {\textbf{\textit{Hobbies: }}Chess, Football, Reading online articles}
          
    \resumeSubHeadingListEnd

\end{document}
